### 2021-02-05 paper/rebuttal/rebuttal.tex

In other words, \emph{word2vec with the negative sampling is a gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
While the gravity model generates the flow from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given trajectories.
Therefore, the embedding distance is inherently tied to the flow, and hence, has greater predictive power than the geographic distance.

\subsection{Some concerns on this section??}
\todo{
Why cosine similarity is better? In-vector and out-vectors are different in our result}

\section{Performance of \textit{word2vec} compared with baselines}
\subsection{The method we have used for the test}
We list baselines that we have used for the validation. For embedding baselines, we set $d=300$ for the pair comparison.\\\\
\textbf{SVD-based embedding baselines}
\begin{itemize}
    \item Truncated SVD on the flow matrix
	\item  Laplacian eigenmap
	\item Levy's word2vec
\end{itemize}
\textbf{Network-based baselines}
\begin{itemize}
    \item Personalized Page Rank
\end{itemize}
\textbf{Geographical baselines}

\subsection{Result}
\todo{report the results and say our results are better @dakoda
}

% why sgd is better?
An issue in the matrix factorization approach is that it is extremely sensitive to small flows between affiliations. The matrix factorization approach embeds affiliations $i$ and $j$ such that their dot similarity is as close as to $\log (T_{ij} / P(i) P(j))$. If the flow $T_{ij}$ is considerably small or zero, the dot similarity goes $-\infty$, pushing $i$ and $j$ too far from the other affiliations in the embedding space~\autocite{levy2014neural, Qui2018}. This is particularly problematic when the window size is small because most affiliation pairs would have no flow, which is indeed the case in our experiments. To circumvent this problem, the previous studies~\autocite{levy2014neural, Qui2018} add a constant flow between the affiliation pairs with no flow. However, this changes the data to which we fit the model, and small flows still have a considerably strong impact on the embedding.

Also, it is well known that SVD by itself is very vulnerable to outliers \autocite{ xu2012robust, huber1981robust, xu1995robust, chandrasekaran2011rank, candes2011robust, }. Compared to SVD, a stochastic gradient descent algorithm (SGD) which is employed in SGNS \textit{word2vec} benefits from the noise in the model itself and can enhance generalization and effectiveness as well \autocite{ma2018power, smith2020generalization, zhang2019algorithmic,}.

### 2021-02-05 paper/rebuttal/rebuttal.tex

\usepackage[style=nature,
					backend=biber,
					sortcites=true,
					autocite=superscript
]{biblatex}

\AtEveryBibitem{%
 \clearfield{url}%
   \clearfield{month}%
 \clearfield{issn}%
 \clearfield{doi}%%
}

\addbibresource{rebuttal.bib}

%
% HEADER
%
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Nature---Response to Reviews}
\rhead{\thepage}
\chead{}

@@

\DeclareUnicodeCharacter{FB01}{fi}
\usepackage{dirtytalk}

\def\figdir{../Figs}

\usepackage[most]{tcolorbox}
\newcommand{\sada}[1]{{\leavevmode\color{orange}[SK: #1]}}
\newcommand{\sadaadded}[1]{{\leavevmode\color{orange}{#1}}}
\newcommand{\todo}[1]{{\leavevmode\color{orange}[TODO: #1]}}
\newcommand{\add}[1]{{\leavevmode\color{blue}#1}}
\newcommand{\del}[1]{{\leavevmode\color{red}\sout{#1}}}
\newcommand{\response}[1]{{\noindent \textbf{Response:} \\ \\ \noindent #1}}
%\newcommand{\rcomment}[1]{{\bigskip\begin{snugshade}\begin{quotation}\noindent #1 \end{quotation}\end{snugshade} }}
\newcommand{\rcomment}[1]{%
\vspace{10pt}
\begin{tcolorbox}[colback=black!3,colframe=white!45!black, left=0pt, right=0pt, top=0pt, bottom=0pt, arc=0pt,outer arc=0pt, grow to left by=-0.5cm,grow to right by=-0.5cm]
#1
\end{tcolorbox}
}
\newcommand{\correction}[2]{{\begin{quotation}\noindent {#1}{\it #2} \end{quotation} }}
%\newcommand{\correction}[2]{{\bigskip\begin{quotation}\noindent {#1}{\it #2} \end{quotation} }}

@@

\newcommand{\mycaption}[2]{%
  \caption[#1]{\textbf{#1} \small#2}%
}
% comment out when submitting
\definecolor{myblue}{RGB}{33,150,243}
\definecolor{mygreen}{RGB}{76, 175, 80}
\definecolor{purple}{RGB}{170, 0, 255}

\makeatletter
\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
\begin{flushleft}
\Large  \textbf{\@title}
\end{flushleft}\egroup
}
\makeatother
\title{Re: Nature submission 2020-10-19515}
\date{}
\begin{document}
\maketitle

\bigskip
\noindent Dear Dr. Mary Elizabeth Sutherland and Referees, \\

We thank all the referees for their incredibly thoughtful and helpful comments and critiques, all of which provided valuable insights. 
Following these comments, we have made a breakthrough in our study, and have made substantial revisions to our manuscript to emphasize these new theoretical contributions and additional methodological comparisons. 
With these changes, we are confident that our paper is significantly stronger, and its contribution more wide-reaching and impactful. 
Again, we are incredibly appreciative of these comments, which provided the insight and motivation needed to make these breakthroughs.

We have developed the mathematical and theoretical basis of our approach for embedding mobility, and made additional updates to our experiments and manuscript, addressing the three main issues raised by referees:

\begin{enumerate}
    \itemsep0em 
	\item Our approach and analysis lacked theoretical justification and grounding, and the application of \textit{word2vec} to mobility was arbitrary
	\item Performance of \textit{word2vec} is not well understood in the context of other, simpler embedding techniques
	\item Our findings were not sufficiently grounded in the literature of neural embeddings and mobility
\end{enumerate}

Addressing the first point, we have identified an underlying mathematical connection between the Gravity Model of Mobility and the neural embedding technique \textit{word2vec}. 
Namely, we demonstrate that \textit{word2vec} implicitly learns gravity-like relationships between entities, whether it be language or locations. 
This development constitutes a major breakthrough in our understanding of neural embeddings, and provides theoretical justification for their application to mobility.

For the second point, we have also conducted experiments comparing the performance of neural embedding to distances from an embedding derived by a singular value decomposition of the mobility network, and of a Laplacian eigenmap embedding. Additionally, we compare \textit{word2vec} model to another matrix factorization approach, which \textit{word2vec} approximates. We find that the embedding distance from \textit{word2vec} outperforms all baselines in explaining and predicting real-world mobility.

Finally, addressing the third point, we take steps to better ground our manuscript in the existing literature, integrating the reviewer's suggested articles into our manuscript.

In the attached detailed response, we outline the connection between \textit{word2vec} and the gravity model (section 1), and comparisons to baselines (section 2). We then provide a point-by-point response to each of the reviewer's comments in section 3.

We thank you for your time, attention, and insight, and look forward to hearing back from you!\\

\\Kind Regards,\\

Dakota, Jisung, Sadamori, Rodrigo, Woo-Sung, Staša, and YY

\clearpage
\tableofcontents
\listoffigures

### 2021-02-05 paper/rebuttal/rebuttal.tex

We thank you for your time, attention, and insight, and look forward to hearing back from you!\\

Kind Regards,

Dakota, Jisung, Sadamori, Rodrigo, Woo-Sung, Staša, and YY

\clearpage
\tableofcontents
\listoffigures
\clearpage

\section{Theoretical justification of \textit{word2vec} and the Gravity Model} 
Here, we attempt to answer a question raised from our analysis: Why does the skip-gram model with negative sampling (SGNS), otherwise known as \textit{word2vec}, work so well to model human mobility?
We demonstrate a fundamental connection between the SGNS model and the Gravity Model of Mobility, namely, that SGNS implicitly learns gravity-like relationships between locations. 
This connection provides necessary theoretical justification to our choice of \textit{word2vec}, and constitutes a major breakthrough of our understanding of neural embeddings. 
In addition, this motivates the use of SGNS for future study of human mobility.

First, we outline of the \textit{word2vec} model. 
Then, we introduce the specific SGNS model, which incorperates a procedure called negative sampling that is key to its connection with the gravity model. 
Finally, we demonstrate the connection between SGNS and the gravity model of mobility.

\subsection{Some concerns on this section??}
\todo{Why cosine similarity is better? Add speculation sentence to paper}
One open question that remains is why the cosine distance between vectors leads to better performance than the dot product, which is what the formla~\ref{eq:flow_w2v_ng0} expect....

\todo{In-vector and out-vectors are different in our result, add something to paper}
Another deviation in our implementation of \textit{word2vec} to mobility is that the in-vector and out-vector is different in out result, whereas they are assumed to be the same in the above derivations...

\subsection{Changes to the manuscript}
\todo{detail addition of above formulas}
\todo{add sentences to paper concerning above issues/speculations, concerns}
\todo{mention re-doing figures with $\gamma = 1$}

%
% SECTION-PERFORMANCE COMPARISONS
%
\section{Performance of \textit{word2vec} compared with baselines}
\subsection{The method we have used for the test}
We list baselines that we have used for the validation. For embedding baselines, we set $d=300$ for the pair comparison.\\\\
\textbf{SVD-based embedding baselines}
\begin{itemize}
    \item Truncated SVD on the flow matrix
	\item  Laplacian eigenmap
	\item Levy's word2vec
\end{itemize}
\textbf{Network-based baselines}
\begin{itemize}
    \item Personalized Page Rank
\end{itemize}
\textbf{Geographical baselines}

%
% SECTION- \POINT-BY-POINT DISCUSSION
%
\section{Point-by-point discussion}
All of the referees presented us with excellent, insightful comments and we feel that the changes implemented as a consequence have signiﬁcantly strengthened the manuscript. Here we offer further discussion, and introduce several results and figures to support certain arguments.

### 2021-02-05 paper/rebuttal/rebuttal.tex

\subsection{Some concerns on this section??}
\todo{Why cosine similarity is better? Add speculation sentence to paper}
One open question that remains is why the cosine distance between vectors leads to better performance than the dot product, which is what the formla~\ref{eq:flow_w2v_ng0} expect....

\todo{In-vector and out-vectors are different in our result, add something to paper}
Another deviation in our implementation of \textit{word2vec} to mobility is that the in-vector and out-vector is different in out result, whereas they are assumed to be the same in the above derivations...

\subsection{Changes to the manuscript}
\todo{detail addition of above formulas}
\todo{add sentences to paper concerning above issues/speculations, concerns}
\todo{mention re-doing figures with $\gamma = 1$}

%
% SECTION-PERFORMANCE COMPARISONS
%
\section{Performance of \textit{word2vec} compared with baselines}
\subsection{Alternatives considered}
In our original manuscript, we compared the performance of what we call the embedding distance---the cosine distance between vectors learned by \textit{word2vec}---to a range of alternatives. 
These alternatives included the geographic distance between locations, the distance most commonly used in definitions of the gravity model of mobility, along with the dot product similarity between embedding vectors, and the cosine distance and Jensen-Shannon divergence between vectors obtained from a personalized-page-ranking procedure on the underlying mobility network.

Following the advice of the referees, we also add additional baselines to illustrate how the embedding distance performs compared to simpler embedding alternatives. 
The first of these baselines uses the distance between vectors in an embedding space produced through a singular-value decomposition of the underlying location co-occurrence matrix.
The second baseline is the distance between vectors obtained through a Laplacian eigenmap embedding of the location of the matrix.

In addition to these suggested baselines, we also consider distances derived from embeddings learned through matrix factorization following the procedure outlined by Levy \& Goldberg~\autocite{levy2014neural}.
The \textit{word2vec} model  implicitly approximates this matrix-factorization procedure, and so comparison to these ``Levy'' distances can demonstrate whether the approximation of neural embeddings outperform direct-calculations.

### 2021-02-05 paper/rebuttal/rebuttal.tex

\AtEveryBibitem{%
 \clearfield{url}%
   \clearfield{month}%
 \clearfield{issn}%
 \clearfield{doi}%%
}

\addbibresource{rebuttal.bib}

%
% HEADER
%
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Nature---Response to Reviews}
\rhead{\thepage}
\chead{}

%
% COLORBOX
%
\usepackage{tcolorbox}
\tcbuselibrary{breakable}
\newtcolorbox[auto counter, 				  
					  number within=subsection,
 				       list type=subsubsection, 
 				       list inside=toc]{sectionbox}[1]{colback=white, 
 				       												colframe=black, 
 				       												colbacktitle=white!50!gray,
 				       												coltitle=black,
 				       												fonttitle=\bfseries, title={Comment \thetcbcounter}, 
 				       												list entry={Comment \thetcbcounter\quad}, breakable}

@@

\DeclareUnicodeCharacter{FB01}{fi}
\usepackage{dirtytalk}

\def\figdir{../Figs}

%\usepackage[most]{tcolorbox}
\newcommand{\sada}[1]{{\leavevmode\color{orange}[SK: #1]}}
\newcommand{\sadaadded}[1]{{\leavevmode\color{orange}{#1}}}
\newcommand{\todo}[1]{{\leavevmode\color{orange}[TODO: #1]}}
\newcommand{\add}[1]{{\leavevmode\color{blue}#1}}
\newcommand{\del}[1]{{\leavevmode\color{red}\sout{#1}}}
\newcommand{\response}[1]{{\noindent \textbf{Response:} \\ \\ \noindent #1}}
%\newcommand{\rcomment}[1]{{\bigskip\begin{snugshade}\begin{quotation}\noindent #1 \end{quotation}\end{snugshade} }}
\newcommand{\rcomment}[1]{%
\vspace{10pt}
\begin{sectionbox}
#1
\end{sectionbox}
}
\newcommand{\correction}[2]{{\begin{quotation}\noindent {#1}{\it #2} \end{quotation} }}
%\newcommand{\correction}[2]{{\bigskip\begin{quotation}\noindent {#1}{\it #2} \end{quotation} }}

@@

In other words, \emph{word2vec with the negative sampling is a gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
While the gravity model generates the flow from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given trajectories.
Therefore, the embedding distance is inherently tied to the flow, and hence, has greater predictive power than the geographic distance.

\subsection{Some concerns on this section??}
\todo{Why cosine similarity is better? Add speculation sentence to paper}
One open question that remains is why the cosine distance between vectors leads to better performance than the dot product, which is what the formla~\ref{eq:flow_w2v_ng0} expect....

\todo{In-vector and out-vectors are different in our result, add something to paper}
Another deviation in our implementation of \textit{word2vec} to mobility is that the in-vector and out-vector is different in out result, whereas they are assumed to be the same in the above derivations...

\subsection{Changes to the manuscript}
To reflect these breakthroughs, we have made the following changes to the manuscript:
\begin{itemize}
	\itemsep0em
	\item Following results demonstrating the performance of the embedding distance compared to geographic distance, we add the section \textbf{word2vec and the gravity model}, which summarizes the link between the two models.
	\item We also added the section \textbf{An implicit bias in the negative sampling} to the methods section of our manuscript.
	\item Since the formulation of the gravity used in the above derivations assumes $\gamma = 1$, we use this value of $gamma$ for all reported results. No result substantively changes with this change.
	\item \todo{We added a sentence to the paper speculating on why cosine similarity works best}
	\item \todo{We also added a sentence noting the in-vector and out-vector issue, and speculating on reasons/consequences}
\end{itemize}

@@

%
% SECTION-PERFORMANCE COMPARISONS
%
\section{Performance of \textit{word2vec} compared with baselines}
\subsection{Alternatives considered}
In our original manuscript, we compared the performance of what we call the embedding distance---the cosine distance between vectors learned by \textit{word2vec}---to a range of alternatives. 
These alternatives included the geographic distance between locations, the distance most commonly used in definitions of the gravity model of mobility, along with the dot product similarity between embedding vectors, and the cosine distance and Jensen-Shannon divergence between vectors obtained from a personalized-page-ranking procedure on the underlying mobility network.

Following the advice of the referees, we also add additional baselines to illustrate how the embedding distance performs compared to simpler embedding alternatives. 
The first of these baselines uses the distance between vectors in an embedding space produced through a singular-value decomposition of the underlying location co-occurrence matrix.
The second baseline is the distance between vectors obtained through a Laplacian eigenmap embedding of the location of the matrix.

In addition to these suggested baselines, we also consider distances derived from embeddings learned through matrix factorization following the procedure outlined by Levy \& Goldberg~\autocite{levy2014neural}.
The \textit{word2vec} model  implicitly approximates this matrix-factorization procedure, and so comparison to these ``Levy'' distances can demonstrate whether the approximation of neural embeddings outperform direct-calculations.

\subsection{New experimental parameters}
In addition to the new baselines, we have also incorporate additional experimental parameters into our analysis. 
The first is $\gamma$, a hyper-parameter of the \textit{word2vec} model, which defines the exponent which shapes the negative sampling distribution.
The default of the `\texttt{gensim} implementation of \textit{word2vec} is to set $\gamma = 0.75$, and this was the value used in our original manuscript. 
However, to connect \textit{word2vec} to the gravity model of mobility, we assume $\gamma = 1.0$ (see section 1). 
We now report all main results using $\gamma = 1.0$, however we also compare its performance to embeddings learned using $\gamma = 0.75$, as we do with the number of embedded dimensions and window size.

We also consider an experimental parameter differentiating between definitions of \textit{population}, in the context of scientific mobility. 
Our original manuscript defined the population of an organization as its average annual number of unique mobile and non-mobile authors who publish with that organizational affiliation. 
However, because non-mobile authors do not have mobility trajectories, and are thus not included in training of the embedding, this definition of population introduces additional, potentially confounding information into the experiment. 
To tease apart the impact of population definitions, we consider two additional definitions.
The first defines an organization's population as the average annual number of unique mobile authors, only, who publish with the organization. 
The second definition defines the population akin to language, as simply its frequency across all mobility trajectories.

@@

\subsection{Result}
\todo{report the results and say our results are better @dakoda
}

\subsection{Why do neural embeddings outperform direct matrix factorization?}% why sgd is better?
An issue in the matrix factorization approach is that it is extremely sensitive to small flows between affiliations. The matrix factorization approach embeds affiliations $i$ and $j$ such that their dot similarity is as close as to $\log (T_{ij} / P(i) P(j))$. If the flow $T_{ij}$ is considerably small or zero, the dot similarity goes $-\infty$, pushing $i$ and $j$ too far from the other affiliations in the embedding space~\autocite{levy2014neural, Qui2018}. This is particularly problematic when the window size is small because most affiliation pairs would have no flow, which is indeed the case in our experiments. To circumvent this problem, the previous studies~\autocite{levy2014neural, Qui2018} add a constant flow between the affiliation pairs with no flow. However, this changes the data to which we fit the model, and small flows still have a considerably strong impact on the embedding.

### 2021-02-08 paper/rebuttal/rebuttal.tex

The flow $\hat{T_{ij}}$ is symmetric (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because {\it word2vec} neglects whether the context $j$ appears before or after the center $i$ in the trajectory -- the mechanism of skip-gram.
If we swap $i$ and $j$ in Eq.~\eqref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
Therefore, to ensure $T_{ij} = T_{ji}$, the denominator $Z_i$ should be a constant.

Taken altogether, the {\it word2vec} model with the negative sampling predicts a flow in the same form as in the gravity model:
\begin{align}
	\hat{T_{ij}}=  C P(i) P(j)  \exp(\bm{v}_j \cdot \bm{v}_{i}), \label{eq:flow_w2v_ng0}
\end{align}
where $C$ is a positive constant.

In other words, \emph{word2vec with the negative sampling is a gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
While the gravity model generates the flow from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given trajectories.
Therefore, the embedding distance is inherently tied to the flow, and hence, has greater predictive power than the geographic distance.

\subsection{Gap between the mathematical analysis and numerical simulations}

In the mathematical analysis, we assumed that the embedding vectors are optimal in terms of the objective of {\it word2vec}, which, however, is not true in our numerical simulations.
This violation of assumption leads to two substantial consequences for embedding vectors.
First, although there exist optimal in-vector and out-vector that are identical, the in-vector and out-vector can be different in practice because they are sub-optimal.
Second, while dot similarity is a formal distance measure in terms of its connection to the gravity model, our simulations show that dot similarity did not predict mobility flow better than cosine similarity (Figs.~\ref{fig:supp:distancemetrics} and \ref{fig:supp:distancemse}). It has been widely observed that cosine similarity is generally better than dot similarity in many applications of word embedding~\cite{} [Jisung, could you add citations?]. Therefore, the superiority of cosine similarity is not a problem specific but general feature of word embedding.
Nevertheless, dot similarity is the second best predictor among the 7 embedding distances. What makes cosine similarity superior to dot similarity warrants the future work.

### 2021-02-09 paper/rebuttal/rebuttal.tex

\section{Theoretical justification of \textit{word2vec} and the Gravity Model}
Here, we attempt to answer a question raised from our analysis: Why does the skip-gram model with negative sampling (SGNS), otherwise known as \textit{word2vec}, work so well to model human mobility?
We demonstrate a fundamental connection between the SGNS model and the Gravity Model of Mobility, namely, that SGNS implicitly learns gravity-like relationships between locations.
This connection provides necessary theoretical justification to our choice of \textit{word2vec}, and constitutes a major breakthrough of our understanding of neural embeddings.
In addition, this motivates the use of SGNS for future study of human mobility.

First, we outline of the \textit{word2vec} model.
Then, we introduce the specific SGNS model, which incorperates a procedure called negative sampling that is key to its connection with the gravity model.
Finally, we demonstrate the connection between SGNS and the gravity model of mobility.

\subsection{Details on \textit{word2vec} algorithm}
We used standard skip-gram negative sampling word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec}.
Suppose a trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), where $a_{t}$ is the $t$th location in the trajectory. A location, $a_{t}$, is considered to have context locations, $a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}$, that appear in the window surrounding $a_t$ up to a time lag of $w$, where $w$ is the window size parameter truncated at $t - w \geq 0$ and $t + w \leq T$. Then, the model learns probability $p(a_{t + \tau} \vert a_{t})$, where $-w\leq \tau\leq w$ and $\tau \neq 0$,  by maximizing its log likelihood given by
%
% MAIN W2V Equation
%
\begin{equation}
	\frac{1}{T}\sum_{t = 1}^{T} \sum_{-w \leq \tau \leq w, \tau \neq 0} \log p(a_{t + \tau} \vert a_{t}),
\end{equation}
where,

%
% CONDITIONAL PROBABILITY EQ
%
\begin{equation}
	p(j \given i) = \frac{\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i}, \label{eq:cond_prob_w2v}
\end{equation}
where $\bm{v}$ and $\bm{u}$ are the ``in-vector'' and ``out-vector'', respectively,  $Z_i=\sum_{j' \in \mathcal{A}} \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$ is a normalization constant, and $\mathcal{A}$ is the set of all locations. In general, calculating $Z_i$ is computationally expensive and there are two common approximation:
hierarchical softmax \autocite{morin2005hierarchical} and negative sampling \autocite{mikolov2013word2vec}.

@@

%
% SECTION- POINT-BY-POINT DISCUSSION
%
\section{Point-by-point discussion}
All of the referees presented us with excellent, insightful comments and we feel that the changes implemented as a consequence have signiﬁcantly strengthened the manuscript. Here we offer further discussion, and introduce several results and figures to support certain arguments.

\subsection{Response to Referee 1}

\rcomment{%
	To the best of my knowledge, this is the first work providing a thorough analysis of the structure encoded by latent mobility embeddings (e.g., the prestige hierarchy), and this is the first work I am aware of to propose embeddings as an explanatory/exploratory tool in this context. In this way, the work has some originality and significance.

	\begin{itemize}
		\item Liu, Xin, Yong Liu, and Xiaoli Li. ``Exploring the Context of Locations for Personalized Location Recommendations.'' IJCAI. 2016.
		\item Feng, Shanshan, et al. ``POI2Vec: geographical latent representation for predicting future visitors.'' AAAI. 2017.
		\item Yao, Zijun, et al. ``Representing Urban Functions through Zone Embedding with Human Mobility Patterns.'' IJCAI. 2018.
		\item Cao, Hancheng, et al. ``Habit2vec: Trajectory semantic embedding for living pattern recognition in population.'' IEEE Transactions on Mobile Computing 19.5 (2019): 1096-1108.
	\end{itemize}

@@

\response{Thank you for this comment. While robustness is a general concern for these methods, we found that their application to our datasets were in fact quite robust, and observed no evidence that findings were the result of methodological artefacts. This is confirmed in extra work done in response to these reviews.

	\noindent We re-ran all of our results using different starting seeds and found all results were qualitatively similar, and almost quantitatively identical.
	In addition, we expanded the set of experimental parameters, training 18 different embeddings with different dimensions, window sizes, and now, $\gamma$.
	We found that while performance varies across each combination of parameters, the main results remain qualitatively similar.
	While we can run more combinations of parameters, and more iterations of \textit{word2vec}, we see no evidence that results will drastically vary.

	\noindent We believe that the ratio of the number of organizations represented in our dataset to the total number of mobility trajectories makes our results especially robust.
	Only about 8,661 organizations are represented across over three million career trajectories of scientists, such that nearly every organization appears enough times, and in enough contexts, to produce a robust vector representation.
	However, this may not hold true for all problem domains—for example, natural language includes many millions of tokens, many of which will occur only a few times, allowing stochasticity to have a much stronger effect on the final representation.
	Heeding this as a general concern, we have added the following sentence to our limitations paragraph in our conclusion:

	\noindent “We however, note that all results shown here are robust to this stochasticity, likely emerging from the limited ``vocabulary'' of scientific mobility, airports, and accommodations (several thousand) and the massive datasets used (several million trajectories). Applications of word2vec to problem domains where the ratio of the vocabulary to data is smaller, however, should take caution to ensure that findings are not the result of random artifacts.”

@@

\rcomment{
	My second group of questions pertain to the prestige hierarchy, that really drives the dynamics of scientific mobility. The technical description addressed most of them. However, I was wondering, is it all possible to go beyond the descriptive part, and show cases where the more accurate embedding base distances do make a difference? That is, using them, we do not only obtain better correlations with the ranking data, but also allows us to address problems that we could not without the embedding distance? For example, some results have shown that a paper coauthored by two authors at different high prestige institutions has higher impact, than writing a paper with two authors of the same high prestige institution—would embedding help us pull apart such effects? Here I am not trying to make the authors to write a different paper, so maybe a little forward thinking may be enough, if doing the actual work is too time consuming, and goes beyond the current narrative.
}

\response{Thank you for this idea!
	We believe that this is an interesting topic and we hope to investigate it in the future.
	In your particular example, an embedding distance trained using sequences of co-authorship on the same paper might be better to capture the \textit{collaborative} distance between institutions.
	Then, using that distance, one could measure the ``embedding distance'' spanned by all authors in the byline, and relate this to questions impact to determine whether (a)typical collaborations relate to impact.
	This is certainly a topic that is in our mind for future study.
	In the case of scientific mobility, we might also consider the ``embedding distance'' spanned by an individual's career, and relate this to their demographics and scientific impact.
